Experiences with Planning for Natural Language Generation

### 2009-06-03 trunk/Papers/ci-spark/experiments.tex
changes to section 4

Results for the $h=20$ case, with $n$ ranging from $1$ to $40$, are shown
in Figure~\ref{fig:give-runtime-minimal}. The most obvious result is that
FF is unable to solve any problems beyond $n=13$ on our experimentation
machine within the memory limit of 1 GB. SGPLAN, on the other hand, solves
instances beyond $n=40$ without major problems. In this case, our
implementation of GraphPlan is unable to find any of these plans. The time
spent on grounding is not a major factor in either planner, probably
because the planners need more time to actually compute the plan---for
instance, the optimal plan for the problem $n=40$ has a length of about
1600 steps. As a concrete example, the following is a minimal plan for the
case of a $2$ by $2$ grid with $2$ buttons for the player to press (i.e.,
$n=1$, $h=2$):

@@

\begin{figure}[t]
\subfloat[(a) Unordered]{\includegraphics[width=7cm]{data/give-minimal.pdf}}
\subfloat[(b) Ordered]{\includegraphics[width=7cm]{data/give2-minimal.pdf}}
  \caption{Results for the unordered and ordered minimal GIVE domains with grid
  height $h=20$. The horizontal axis is the grid width, $b = 2n$. The
  vertical axis is the total runtime in seconds.}
  \label{fig:give-runtime-minimal}
\end{figure}

@@

\begin{figure}[t]
\subfloat[(a) Unordered]{\includegraphics[width=7cm]{data/give-extracells.pdf}}
\subfloat[(b) Ordered]{\includegraphics[width=7cm]{data/give2-extracells.pdf}}
  \caption{Results for the unordered and ordered GIVE domains with $h = 20$ and
  $n = 10$. The horizontal axis is the extra grid width $w$.
  The vertical axis is the total runtime in seonds.}
  \label{fig:give-extracells}
\end{figure}

\begin{figure}[t]
\subfloat[(a) Unordered]{\includegraphics[width=7cm]{data/give-button-unord.pdf}}
\subfloat[(b) Ordered]{\includegraphics[width=7cm]{data/give-button-ord.pdf}}
  \caption{Results for the unordered and ordered GIVE domains with a grid size
  of height 20 and width 40. The horizontal axis is the number of buttons $b$.
  The vertical axis is the runtime in seonds.}
  \label{fig:give-buttons}
\end{figure}

>>>>

Results for the $h=20$ case, with $n$ ranging from $1$ to $40$, are shown
in Figure~\ref{fig:give-minimal}. The most obvious result is that
FF is unable to solve any problems beyond $n=13$ on our experimentation
machine within the memory limit of 1 GB. SGPLAN, on the other hand, solves
instances beyond $n=40$ without major problems. In this case, our
implementation of GraphPlan is unable to find any of these plans. The time
spent on grounding is not a major factor in either planner, probably
because the planners need more time to actually compute the plan---for
instance, the optimal plan for the problem $n=40$ has a length of about
1600 steps. As a concrete example, the following is a minimal plan for the
case of a $2$ by $2$ grid with $2$ buttons for the player to press (i.e.,
$n=1$, $h=2$):

@@

\begin{figure}[t]
\subfloat[(a) Unordered]{\includegraphics[width=7cm]{data/give-minimal.pdf}}
\subfloat[(b) Ordered]{\includegraphics[width=7cm]{data/give2-minimal.pdf}}
  \caption{Results for the unordered and ordered minimal GIVE domains with grid
  height $h=20$. The horizontal axis is the grid width, $b = 2n$. The
  vertical axis is the total runtime in seconds.}
  \label{fig:give-minimal}
\end{figure}

\begin{figure}[t]
\subfloat[(a) Unordered]{\includegraphics[width=7cm]{data/give-minimal-grounding.pdf}}
\subfloat[(b) Ordered]{\includegraphics[width=7cm]{data/give2-minimal-grounding.pdf}}
  \caption{Comparison of the total running time and grounding time for selected
  planners in the $h=20$ minimal GIVE domain. The horizontal axis is the grid
  width, $b = 2n$. The vertical axis is the total runtime in seconds.}
  \label{fig:give-minimal-grounding}
\end{figure}

@@

\begin{figure}[t]
\subfloat[(a) Unordered]{\includegraphics[width=7cm]{data/give-extracells.pdf}}
\subfloat[(b) Ordered]{\includegraphics[width=7cm]{data/give2-extracells.pdf}}
  \caption{Results for the unordered and ordered GIVE domains with $h = 20$ and
  $n = 10$. The horizontal axis is the extra grid width $w$.
  The vertical axis is the total runtime in seconds.}
  \label{fig:give-extracells}
\end{figure}

\begin{figure}[t]
\subfloat[(a) Unordered]{\includegraphics[width=7cm]{data/give-button-unord.pdf}}
\subfloat[(b) Ordered]{\includegraphics[width=7cm]{data/give-button-ord.pdf}}
  \caption{Results for the GIVE domains with a fixed grid size of
  height 20 and width 40. The horizontal axis is the number of buttons $b$.
  The vertical axis is the runtime in seconds (log scale).}
  \label{fig:give-buttons}
\end{figure}
